### 2025-07-03 Text/Thesis/Chapters/Chapter3.qmd
update derivations in main text

## Optimal $\lambda$ Selection 
<!-- Finding the Optimal Value of $\lambda$ for the Rényi and Tsallis Entropy Estimators -->

@@

```{r fig-densities-shannon, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.pos="hbt", fig.cap="Empirical densities of $S_{\\widetilde{H}_{AO}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$.", fig.width=9, fig.height=4.0}

@@

```{r fig-densities,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="80%", fig.pos="hbt",  fig.cap="Empirical densities of $S_{\\widetilde{R}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$, with $\\lambda=0.9$.", fig.width=9, fig.height=4.0}
#fig.show="hide", 
# eval=FALSE,  #

@@

```{r fig-densities-tsallis4,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="80%", fig.pos="H",  fig.cap="Empirical densities of $S_{\\widetilde{T}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$, with $\\lambda=0.85$.", fig.width=9, fig.height=4.0}
#fig.show="hide", 
# eval=FALSE,  #

@@

```{=latex}
\begin{figure}[H]
    \centering
\begin{tikzpicture}[
  node distance=1cm and 1cm,
  box/.style={
    rectangle, draw=black, fill=teal!20,
    minimum width=3cm, minimum height=1cm,
    align=center, font=\small, text=black, font=\bfseries
  },
  arrow/.style={
    -{Stealth[length=2mm, width=1.2mm]},
    semithick,
    shorten >=1pt, shorten <=1pt
  }
]
  \node[box] (raw) {1. Compute\\test statistic\\ $S(\bm{Z})$};
  \node[box,right=of raw] (std) {2. Standardize\\ $\varepsilon=(S-\hat\mu_S)/\hat\sigma_S$};
  \node[box,right=of std] (pval) {3. Compute \\ $2\Phi(-|\varepsilon|)$};
  \node[box,right=of pval] (dec) {4. Reject if\\ $p<0.05$};

  \draw[arrow] (raw)  -- (std);
  \draw[arrow] (std) -- (pval);
  \draw[arrow] (pval) -- (dec);
\end{tikzpicture}
    \caption{Workflow of the entropy‐based hypothesis test: compute statistic, standardize, derive $p$-value, and decision by threshold $0.05$.}
    \label{fig:entropy-diagram-test}
\end{figure}

>>>>

### Optimal $\lambda$ Selection 
<!-- Finding the Optimal Value of $\lambda$ for the Rényi and Tsallis Entropy Estimators -->

@@

```{r fig-densities-shannon, echo=FALSE, message=FALSE, warning=FALSE, out.width="90%", fig.pos="hbt", fig.cap="Empirical densities of $S_{\\widetilde{H}_{AO}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$.", fig.width=9, fig.height=4.0}

@@

```{r fig-densities,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="90%", fig.pos="hbt",  fig.cap="Empirical densities of $S_{\\widetilde{R}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$, with $\\lambda=0.9$.", fig.width=9, fig.height=4.0}
#fig.show="hide", 
# eval=FALSE,  #

@@

```{r fig-densities-tsallis4,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="90%", fig.pos="H",  fig.cap="Empirical densities of $S_{\\widetilde{T}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$, with $\\lambda=0.85$.", fig.width=9, fig.height=4.0}
#fig.show="hide", 
# eval=FALSE,  #

@@

```{=latex}
\begin{figure}[H]
    \centering
\begin{tikzpicture}[
  node distance=1cm and 1cm,
  box/.style={
    rectangle, draw=black, fill=teal!20,
    minimum width=3cm, minimum height=1cm,
    align=center, font=\small, text=black, font=\bfseries
  },
  arrow/.style={
    -{Stealth[length=2mm, width=1.2mm]},
    semithick,
    shorten >=1pt, shorten <=1pt
  }
]
  \node[box] (raw) {1. Calculate\\test statistic\\ $S(\bm{Z})$};
  \node[box,right=of raw] (std) {2. Standardize\\test statistic\\ $\varepsilon=(S-\hat\mu_S)/\hat\sigma_S$};
  \node[box,right=of std] (pval) {3. Compute \\ $p$-value \\ $2\Phi(-|\varepsilon|)$};
  \node[box,right=of pval] (dec) {4. Make decision\\Reject if\\ $p<0.05$};

  \draw[arrow] (raw)  -- (std);
  \draw[arrow] (std) -- (pval);
  \draw[arrow] (pval) -- (dec);
\end{tikzpicture}
    \caption{Workflow of the entropy‐based hypothesis test: calculate test statistic, standardize, derive $p$-value, and make a decision by threshold $0.05$.}
    \label{fig:entropy-diagram-test}
\end{figure}
